---
title: "Visualization_1"
author: "Shan Jiang"
date: "9/27/2018"
output: html_document
---
## Lecture Tips
*Dataviz tips*:
 * 3D is bad, make sure the color is distinguished from the each other;
 * Never use the pie chart;
 * Use Color to highlight groups;
 * Do use the Common Axes;
 * Good figures are not necessarily the publication quality pictures;
Why ggplot:
 * "Relative" is compared with the base R graphics;
 * Much easier and much more convinient; 
 * Learning curve for ggplot2/lattice(another package) is needed;
learning ggplot:
 * Stackoverflow;
Using ggplot:
 * data tidy issue is linked affects the ability to visualize 
 
gg = grammar of graphics
Basic graph components:
* data
* aesthetic mappings
* geoms

Advanced graph components:
*facets
*scales
*statistics

A graph is built by combining these components 

**Git repo for visualizing the data** 

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(rnoaa)
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

knitr::opts_chunk$set(echo = TRUE)
```

* the t means temp and is measured in celsuis degree.

#start a plot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```
* you can pipe directly and don't need to sepcify about the data name
```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) %>% +
  geom_point()
```
## More Plot options
```{r}
plot_weather = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) 

plot_weather + geom_point()
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```
## Add a geom _line for the graph
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)
geom_smooth()
```
* alpha blending level - transparent/ not transparent 

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .2) +
  geom_smooth(se = FALSE)
```
* Create every line not a global line   
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .1) +
  geom_smooth(aes(color = name),se = FALSE)
```
Facetting...
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .1) +
  geom_smooth(aes(color = name), se = FALSE) +
 facet_grid(~ name)
```
A more interesting plot / use the date as x.
```{r}
ggplot(weather_df, aes(x = date, y= tmax, color = name, size = prcp)) +
  geom_point() +
  geom_smooth(se = FALSE)+
  facet_grid(~ name)
```
# Create a Geom_hex
```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```
**Tricks in color and definitions for variables in aes**
```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```


##univariate plots
```{r}
ggplot(weather_df, aes(x = tmax)) +
  geom_histogram()
```

```{r}
ggplot(weather_df, aes(x = tmax)) +
  geom_histogram()+
  facet_grid(~name)
```
Hist in smooth
```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) +
  geom_density(alpha = .5)
```
Boxplots!!
```{r}
ggplot(weather_df, aes(x = tmax, y =tmax, fill = name)) +
  geom_boxplot(alpha = .5) 
```

* violin plots for group comparison 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, fill = name)) +
  geom_violin(alpha = .5) 
```
ridges plot
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```
## gg save for saving the document 
```{r}
weather_plot = ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
ggsave("weather plot.png", weather_plot, width = 8, height = 5)
```

* adjust the file size 
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```













