---
title: "Visual 2"
author: "Shan Jiang"
date: "10/2/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Revisiting the examples in the last course
make a bunch of plots!

```{r}
library(tidyverse)
# import the data.
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```
Make a violin plot.
```{r}
ggplot(weather_df, aes(y = prcp  , x = name )) +
  geom_violin()
```

Make a boxplot is more suitable.
```{r}
ggplot(weather_df, aes(y = prcp  , x = name )) +
  geom_boxplot()
```

More information on the density graph.
```{r}
weather_df %>% 
  filter(prcp > 0 ) %>% 
  ggplot(weather_df, aes(x = prcp, fill = name )) +
  geom_density(alpha = .5)
```
## start a plot

First scatter plot; Add labels.
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point(aes(color=name),alpha = .5) +
  geom_smooth(se = FALSE) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  )
```

Tick marks and labels...
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point(aes(color=name),alpha = .5) +
  geom_smooth(se = FALSE) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +  ##labels can only use characters
  scale_x_continuous(
    breaks = c(-15, 0, 15),
    labels = c("-15ºc", "0ºc", "15ºc"),
    limits = c(-29, 40)
  ) + ## position and location of graph on the axis 
  scale_y_continuous(
    position = "right",
    trans = "sqrt" 
  )

```
# colors and themes
Adjust color 
```{r}

ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point(aes(color=name),alpha = .5) +
  geom_smooth(se = FALSE) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +  ## scale color to look at
  scale_color_hue(
    name = "Location", ## name for tuli
    h = c(100, 350),
    l = 50 )
```
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point(aes(color=name),alpha = .5) +
  geom_smooth(se = FALSE) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +  ## scale color to look at
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  )+
  theme(legend.position = "bottom")
## continuous as defalut, change it
```

## Themes
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))+
  geom_point(aes(color=name),alpha = .5) +
  geom_smooth(se = FALSE) +
  labs(
    title = "Temperature plot",
    x = "Minimum daily temperature (C)",
    y = "Maxiumum daily temperature (C)",
    caption = "Data from the rnoaa package"
  ) +  ## scale color to look at
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  )+ 
  theme_bw()+
  theme(legend.position = "bottom")
## We have goot classic themes and also other themes, they just change the theme of the graph.
## theme_bw would overwrite everything after you!
```
* For the color = name, including the color = name in the ggplot, then would get three different lines, but for geom_smooth, it would just be the one line.

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) +
  labs(
    title="Daily Max temperature ",
    x = "Date",
    y = "Temperature(ºc)",
    caption = "Data from moaa package")+ 
  viridis::scale_color_viridis(
    name = "Location", 
    discrete = TRUE
  )+ 
   theme(legend.position = "bottom")
```
## Arguments to `geom_*`
```{r}
centralpark_df <- weather_df %>%  filter(name == "CentralPark_NY")
wakiki_df <-  weather_df %>%  filter(name == "Waikiki_HA")

# ADDing a layer = add a new data set for the graph
ggplot(wakiki_df, aes(x = date, y= tmax)) +
  geom_point() +
  geom_line(data = centralpark_df)
# The same type of graph, like both are points are all work together.
```
## Patchwork

```{r}
devtools::install_github("thomasp85/patchwork")
```

* Individually and stack them, collect the plots. 
plot/ box/ his/ combination as patchwork. Three different panels. 
* facet ~ name means the same panel using the same type of graph. 
Repeat all the graph.
```{r}
tmax_tmin_p = ggplot(weather_df, aes(x = tmax, y = tmin, color = name)) + 
  geom_point(alpha = .5) +
  theme(legend.position = "none")

prcp_dens_p = weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name)) + 
  geom_density(alpha = .5) + 
  theme(legend.position = "none")

tmax_date_p = ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) + 
  theme(legend.position = "bottom")
```
# Patchwork: under development, then we can combine the graph.
```{r}
library(patchwork)
tmax_date_p + tmax_tmin_p / prcp_dens_p 
```

# Data manipulation

factors...

```{r}
ggplot(weather_df, aes(x= name, y =tmax, fill = name))+
  geom_violin()
```
 * change the order appeared in the graph. By using the code of *forcats*
```{r}
weather_df %>%
  mutate(name = forcats::fct_relevel(name, c("Waikiki_HA", "CentralPark_NY", "Waterhole_WA"))) %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .8) + 
  theme(legend.position = "bottom") 
  
```
* order makes it easy for  categorial  variable, voilin are all increasing/ decreasing. 


## data challenging 
```{r}
weather_df %>%
  select(name, tmax, tmin) %>% 
  gather(key = observation, value = temp, tmax:tmin) %>% 
  ggplot(aes(x = temp, fill = observation)) +
  geom_density(alpha = .5) + 
  facet_grid(~name) + 
  viridis::scale_fill_viridis(discrete = TRUE)
```



